Educational attainment and intergenerational mobility: A polygenic score analysis

### 2025-01-08 posts/RustichiniIaconoLeeMcGue/RILM_PGSEdu_JPE2023.qmd
added RILM_PGSEdu_JPE2023.html

    footer: <http://seiroito.github.io/RILM_PGSEdu_JPE2023.html>
    css: ../../../../seiro.css

@@

    theme: [sky, sky-add]

@@

      - ../../../../toc-slide.html
    include-after-body: ../../../../toc-add.html

@@

  file: ../../../../MathShorthand.html 
bibliography: c:/seiro/docs/seiro.bib
#### ../../../../seiro.bib

>>>>

    footer: <http://seiroito.github.io/QuartoFiles/posts/BarthPapageorgeThom/RILM_PGSEdu_JPE2023.html>
    css: ../seiro.css

@@

    theme: [sky]

@@

      - ../toc-slide.html
    includes:
      in_header: ../sky_add_FilePointer.html
      after-body: ../toc-add.html

@@

  file: ../MathShorthand.html 
#### copy c:/seiro/docs/MathShorthand.html ../MathShorthand.html
bibliography: ../seiro.bib
#### ../../../../../seiro.bib
#### copy c:/seiro/docs/seiro.bib ../seiro.bib
